\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-30 manuscript.Rmd
tz-tibble working

# descriptives.data%>%
#   tbl_summary(
#     label = slypos_demographics_tz.factor ~ "Time zone - Country",
#     statistic = list(all_categorical() ~ "{n} ({p}%)"),
#     missing = "no",
#     sort = all_categorical() ~ "frequency",
#     include = "slypos_demographics_tz.factor"
#   )  %>% bold_labels() %>% 
#   modify_header(label ~ "") %>%
#   as_tibble(format = 'pipe') -> tz_tibble

>>>>

descriptives.data%>%
  tbl_summary(
    label = slypos_demographics_tz.factor ~ "Time zone - Country",
    statistic = list(all_categorical() ~ "{n} ({p}%)"),
    missing = "no",
    sort = all_categorical() ~ "frequency",
    include = "slypos_demographics_tz.factor"
  )  %>% bold_labels() %>%
  modify_header(label ~ "") %>%
  as_tibble(format = 'pipe') -> tz_tibble
